### 2016-06-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
New east dimensioned drawing, removed annotation from BDP roof vent photo for gas burner report
Added functionality to plot.py to create data sets where t=0 at ignition for gas burner experiments

\begin{figure}[!ht]
	\includegraphics[width=0.45\columnwidth]{../Figures/Pictures/doorway_BDPs}
	\\~\\
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array at the south exterior doorway (top) and roof vent (bottom) of the East Structure.}
	\label{fig:BDP_arrays}
\end{figure}

@@

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    N/A  		&  	   N/A        \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Old table layout --- will delete soon
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% Old table layout --- will delete soon
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
	\includegraphics[width=0.45\columnwidth]{../Figures/Pictures/doorway_BDPs}
	\\~\\
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs}
	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array at the south exterior doorway (top) and roof vent (bottom) of the East Structure.}
	\label{fig:BDP_arrays}
\end{figure}

@@

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}. Blevins found that the percent error in the measured upper layer temperature for a 1~mm bare-bead thermocouple is bounded by a maximum of 20~\%~\cite{Blevins:1999}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%. ***\textit{Still need to finish reviewing literature about TC uncertainty and add list of components of standard uncertainty along with description about uncertainty estimate.}***

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	~(1)~ All burners on 				& 	0			  &	   1230			&	   2430		\\
	~(2)~ Roof vent opened 				&   128			  &    1320			&	   2520		\\
	~(3)~ West double door opened 		&	153			  &	   1410	 		&	   2610 	\\
	~(4)~ East double door opened 		&   333			  &    1500			&	   2700		\\
	~(5)~ Roof vent closed		 		&   420			  &    1695			&	   2833		\\
	~(6)~ All burners off 				&   550			  &    1815			&	   2970		\\
	~(7)~ Roof vent opened				& 	695 		  &	   1860			&	   3060		\\
	~(8)~ East double door closed		& 	1127 		  &	   2288			&	   N/A		\\
	~(9)~ West double door closed		& 	1140 		  &	   2305			&	   N/A		\\
	(10) Roof vent closed		 		&   1155		  &    2364			&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Seq. 1}	& \textbf{Seq. 2} 	& \textbf{Seq. 3} 	\\
	\midrule
	~(1)~ All burners on 				&	0				&	570				&	1080			\\
	~(2)~ West double door opened 		&	90				&   660				&	1170			\\
	~(3)~ Roof vent opened 		    	&	180				&	720 			& 	1260 			\\
	~(4)~ All burners off 				&	300				&   840				&	1350			\\
	~(5)~ East double door opened		&	345				&   885				&	1420			\\
	~(6)~ Roof vent closed 				&	470				&   1016			&	N/A				\\
	~(7)~ East double door closed		&	497 			&	986				&	N/A 			\\
	~(8)~  West double door closed		&	513 			&	999				&	N/A				\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   127		  		&    116		\\
	~(3)~  1st floor west double door opened 	&	247		  		&    238 	 	\\
	~(4)~  1st floor east double door opened 	&   382			  	&    356		\\
	~(5)~  2nd floor east double door opened	&   517			  	&    484		\\
	~(6)~  PPV fan on 							&   587			  	&    596		\\
	~(7)~  PPV fan off              			&   731			  	&    746		\\
	~(8)~  All burners off 						&   757			  	&    776		\\
	~(9)~  2nd floor south exterior door opened &   836			  	&    836		\\
	(10) PPV fan on 	 						&   997			  	&    926		\\
	(11) 2nd floor south exterior door closed   &   1113		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   120		  		&    110		\\
	~(3)~ 1st floor west double door opened 	&	240		  		&    241 	 	\\
	~(4)~ 2nd floor west double door opened 	&   360			  	&    350		\\
	~(5)~ 2nd floor south exterior door opened	&   480			  	&    470		\\
	~(6)~ PPV fan on 							&   600			  	&    590 		\\
	~(7)~ All burners off 						&   720 		  	&    710		\\
	~(8)~ 2nd floor east double door opened 	&   855			  	&    830		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
